---
title: "First Markdown"
output: 
  html_document:
    toc: true
    toc_float: true
date: "`r Sys.Date()`"
---

Today is `r Sys.Date()`


```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE,warning = FALSE, message = FALSE)
library(tidyverse)
library(easystats)
library(MASS)
```
# MPG Modeling
## data
Using the data from the MPG dataset, we can make a model to show us an estimate for the MPG of different cars based on certain factors.

Here is a sample of the data being used for this.
```{r}
head(mpg)
```
## Graph
We can graph this data to look at trends across certain variables like this

```{r}
mpg %>% ggplot(aes(x=displ,y=hwy, color = factor(cyl)))+
  geom_point()+
  facet_wrap(mpg$year)+
  theme_minimal()+
  geom_smooth(method = "lm")
```

Using general linear regression we can find a model that gives a decent prediction
```{r include=FALSE}
mod <- glm(data= mpg, formula =hwy ~ year*cyl*displ)
better_mod <- stepAIC(mod)
```



```{r}
df <- better_mod %>% broom::tidy()
```